Analytic Doppler Imaging

### 2019-08-15 tex/ms.tex
reorg; spotstar

\newcommand{\D}{D}
\newcommand{\Doppler}{\bvec{D}}
\newcommand{\Surf}{\mathcal{S}}
\newcommand{\Curve}{\mathcal{C}}
\newcommand{\Dargs}{\bvec{d}}
\newcommand{\lmax}{\ensuremath{l_\mathrm{max}}}
\newcommand{\vogtstar}{\texttt{VOGTSTAR}\xspace}

@@

\section{The VOGTSTAR}
\label{sec:vogtstar}

@@

\begin{figure}[p!]
    \begin{centering}
    \includegraphics[width=0.49\linewidth]{figures/vogtstar_u_timeseries.pdf}
    \includegraphics[width=0.49\linewidth]{figures/vogtstar_u_rect.pdf}
    \oscaption{vogtstar_u}{%
        Solution to the \vogtstar problem at high SNR when both 
        the rest frame spectrum and the baseline are known.
        \label{fig:vogtstar_u}
    }
    \end{centering}
\end{figure}

\begin{figure}[p!]
    \begin{centering}
    \includegraphics[width=0.49\linewidth]{figures/vogtstar_ub_timeseries.pdf}
    \includegraphics[width=0.49\linewidth]{figures/vogtstar_ub_rect.pdf}
    \\[0.5em]
    \includegraphics[width=0.405\linewidth]{figures/vogtstar_ub_baseline.pdf}
    \includegraphics[width=0.575\linewidth]{figures/vogtstar_ub_coeffs.pdf}
    \oscaption{vogtstar_ub}{%
        Similar to Figure~\ref{fig:vogtstar_u}, but assuming the baseline
        is not known.
        \label{fig:vogtstar_ub}
    }
    \end{centering}
\end{figure}

\begin{figure}[p!]
    \begin{centering}
    \includegraphics[width=0.49\linewidth]{figures/vogtstar_ubvT_timeseries.pdf}
    \includegraphics[width=0.49\linewidth]{figures/vogtstar_ubvT_rect.pdf}
    \\[0.5em]
    \includegraphics[width=0.405\linewidth]{figures/vogtstar_ubvT_baseline.pdf}
    \includegraphics[width=0.575\linewidth]{figures/vogtstar_ubvT_coeffs.pdf}
    \\[0.5em]
    \includegraphics[width=0.98\linewidth]{figures/vogtstar_ubvT_spectrum.pdf}
    \oscaption{vogtstar_ubvT}{%
        Similar to Figure~\ref{fig:vogtstar_u}, but assuming we have no
        information about either the spectrum, the baseline, or the map
        coefficients.
        \label{fig:vogtstar_ubvT}
    }
    \end{centering}
\end{figure}

\begin{figure}[h!]
    \begin{centering}
    \includegraphics[width=0.98\linewidth]{figures/inclinations.pdf}
    \oscaption{inclinations}{%
        Recovered \vogtstar map as a function of inclination.
        \label{fig:inclinations}
    }
    \end{centering}
\end{figure}

>>>>

\newcommand{\D}{D}
\newcommand{\Doppler}{\bvec{D}}
\newcommand{\Surf}{\mathcal{S}}
\newcommand{\Curve}{\mathcal{C}}
\newcommand{\Dargs}{\bvec{d}}
\newcommand{\lmax}{\ensuremath{l_\mathrm{max}}}
\newcommand{\spot}{\texttt{SPOT}\xspace}

@@

\section{The SPOT star}
\label{sec:spotstar}

@@

\begin{figure}[p!]
    \begin{centering}
    \includegraphics[width=0.49\linewidth]{figures/spot_y1_timeseries.pdf}
    \includegraphics[width=0.49\linewidth]{figures/spot_y1_rect.pdf}
    \oscaption{spot_y1}{%
        Solution to the \spot problem at high SNR when both 
        the rest frame spectrum and the baseline are known.
        \label{fig:spot_y1}
    }
    \end{centering}
\end{figure}

\begin{figure}[p!]
    \begin{centering}
    \includegraphics[width=0.49\linewidth]{figures/spot_y1b_timeseries.pdf}
    \includegraphics[width=0.49\linewidth]{figures/spot_y1b_rect.pdf}
    \\[0.5em]
    \includegraphics[width=0.405\linewidth]{figures/spot_y1b_baseline.pdf}
    \includegraphics[width=0.575\linewidth]{figures/spot_y1b_coeffs.pdf}
    \oscaption{spot_y1b}{%
        Similar to Figure~\ref{fig:spot_y1}, but assuming the baseline
        is not known.
        \label{fig:spot_y1b}
    }
    \end{centering}
\end{figure}

\begin{figure}[p!]
    \begin{centering}
    \includegraphics[width=0.49\linewidth]{figures/spot_y1bs_timeseries.pdf}
    \includegraphics[width=0.49\linewidth]{figures/spot_y1bs_rect.pdf}
    \\[0.5em]
    \includegraphics[width=0.405\linewidth]{figures/spot_y1bs_baseline.pdf}
    \includegraphics[width=0.575\linewidth]{figures/spot_y1bs_coeffs.pdf}
    \\[0.5em]
    \includegraphics[width=0.98\linewidth]{figures/spot_y1bs_spectrum.pdf}
    \oscaption{spot_y1bs}{%
        Similar to Figure~\ref{fig:spot_y1}, but assuming we have no
        information about either the spectrum, the baseline, or the map
        coefficients.
        \label{fig:spot_y1bs}
    }
    \end{centering}
\end{figure}

\begin{figure}[h!]
    \begin{centering}
    \includegraphics[width=0.98\linewidth]{figures/inclinations.pdf}
    \oscaption{inclinations}{%
        Recovered \spot map as a function of inclination.
        \label{fig:inclinations}
    }
    \end{centering}
\end{figure}
